\textbf{Spatio-temporal distinct patterns in variations of \(PM_{10}\) and \(PM_{2.5}\) relative to the recent drivings of emission sources in Mongolia}

### 2024-11-22 submission/manuscript.Rmd
draft processing

Munkh\^1, Joeseph P. Schmo\^2, Sally J. Rivers\^1, Patrick D.
Schloss^1^$\dagger$

@@

$\dagger$ To whom correspondence should be addressed:
[pschloss\@umich.edu](mailto:pschloss@umich.edu){.email}

1\. Department of Microbiology and Immunology, University of Michigan,
Ann Arbor, MI 48109

2\. Other department contact information

@@

## Results
### The spatio-temporal variations of the PMs at the study sites
To comparatively examine the spatio-difference regarding to the emissions of PMs, we illustrated the hourly observed values of PM10 and PM2.5 for all sites (figure_3). On each site, PM10 is more sporadic than PM2.5 due to dust epidemic nature. In conjunction, the mean values averaged from hourly values are larger than its median concentrations both on PM10 and PM2.5 for all sites. The mean variables of p-value show that concentrations of particulate matters significantly differ with 99% confident levels at all sites (figure_3), except  95% confident level between DZ and UB on PM10 (figure_3a). It clearly exhibits general variations of particulate matters as expected and emphasizes that the significant difference in the concentration values among the sites. Besides all sites are quantitatively differ by the values of concentrations in particulate matters, there are two main characteristics can be seen when we compare the median deviations from its mean values etc.

- such patterns are strongly manifested in ZU and SS sites.  
- the mean values those averaged from hourly concentrations of PM10 and PM2.5 is larger than its median are strongly manifested for all in UB and DZ sites.
- Additionally, consider the significance of the ..

This highlight that the fine and coarse particulate matters significantly vary among sites of urban and rural sites, and even within Gobi (rural) sites.
Moreover, .... has a diversely characteristically diversified in respect with the PM2.5 (fine) to PM10 (coarse) particulates.,. which requires urban impacts

To reveal the natural and anthropogenic impacts on the concentrations of particulate matters, we demonstrated annual variations of PM10 and PM2.5 for each sites (figure_4).
3.  Do PM2.5 particulates has contributed to the PM10 annual
    variations?
      Distinct temporal variations has existed among the sites.
        -   PM2.5 particulates has contributed to the PM10 annual
            variations in UB and in DZ in winter.
            -   If yes, how much, and when and where?
            -   What is the sd, mean, and median
                -   box plot
                -   violin
                -   scatter points, epidemic, sporadic
            -   Daily variations to examine it related to the heating
                -   2 peaks: smaller and bigger
                -   compare the t-duration exceeds 50mug/m3/hour

[Therefore] SS and ZU sites are mainly affected by the spring dust, followed by the autumn dust. Annual maximum in the winter for DZ and UB are from PM2.5, which results an increase in PM10.
It requires the cause the behind such the variations. DZ site is polluted in the winter by the heating and in the spring by the natural dust.

[Therefore] Spatio-temporally in two class; consists of 2 Gobi sites, and 1 urban plus urbanized Gobi sites.

@@

>>>>

Munkhtsetseg\^1\^5$^*$, Shimizu. A\^2, Matsuki. A\^3, Batdorj. D\^4,
Matsui. H^1$^*$

@@

$^*$ To whom correspondence should be addressed:
[e.munkhtsetseg\@yahoo.com](mailto:e.munkhtsetseg@yahoo.com){.email}

1\. Nagoya University, Japan

2\. NIES

@@

## Results
### The spatio-temporal variations of the PMs at the study sites
To evaluate the spatial variations in particulate matter (PM) concentrations, we displayed hourly observed values of PM10 and PM2.5 for all study sites (figure_3). The mean p-values indicate that PM concentrations differ significantly at a 99% confidence level across all sites (figure_3), with the exception of a 95% confidence level between DZ and UB for PM10 (figure_3a), highlighting substantial concentration disparities among sites. While quantitative differences in PM concentration values exist across all sites, two key patterns emerge when examining median deviations from mean values and irregular observation fluctuations. For instance, PM10 demonstrates more erratic behavior than PM2.5 at each location, particularly evident at ZU and SS sites. Furthermore, the mean values calculated from hourly measurements surpass the median concentrations for both PM10 and PM2.5 across all sites, with notable prominence at UB and DZ locations. Consequently, significant spatial differences in PM concentrations exist among all sites, regardless of urban or rural classification. However, the sites can be categorized into two groups based on their characteristics: UB (urban) and DZ (rural town, Gobi); and SS (rural, Gobi) and ZU (rural, Gobi). These findings for DZ appear to support our hypothesis of emerging new emission patterns related to increased coal consumption during winter months.
---
[AND] To examine the PM emerging patterns whether it related to household heating fuel, we demonstrated annual variations in PM10 and PM2.5 concentrations at the sites.
[AND] Significant annual variations in PM10 and PM2.5 levels demonstrating higher concentrations in colder months and lower concentrations in warmer months at UB and DZ sites.

[AND] During colder months (January, November, December), PM10 concentrations contributed by elevated levels in PM2.5 were exceed 100 $\mu g/m^3$, accompanied by PM10 and PM2.5 concentrations reached their lowest points during warmer months (May-September), with medians and ranges consistently below 50 $\mu g/m^3$. This distinct seasonal trend, peaking during the same cold months are supported by the diurnal variations in PM10 and PM2.5 concentrations at sites DZ and UB. A pronounced daily cycle is evident, at both DZ and UB sites, where PM concentrations peak during nighttime and early morning hours (approximately 8 PM to 4 AM UTC), with median values surpassing 50 $\mu g/m^3$. PM2.5 concentrations consistently follow a similar pattern but remain lower than PM10. In contrast, both pollutants exhibit reduced concentrations during daytime hours (8AM to 4PM UTC), likely due to increased atmospheric dispersion. At site UB, a comparable daily trend is observed, but with lower overall concentrations and less pronounced peaks. The variability, indicated by the interquartile range, is higher during nighttime, suggesting the influence of localized emission sources and reduced boundary layer mixing. These diurnal patterns underscore the temporal dynamics of air pollution, influenced by both anthropogenic activities and meteorological conditions.

Analysis of PM10 and PM2.5 concentrations revealed that ZU and SS maintained significantly lower levels throughout the year, while UB and DZ exhibited higher concentrations, especially during colder months. The consistently lower particulate matter levels at ZU and SS suggest localized differences in pollution sources and dispersion patterns. These results underscore the seasonal and spatial variability in air quality, likely influenced by meteorological conditions and human activities.  The observed seasonal patterns in PM10 and PM2.5 concentrations may be attributed to changes in weather conditions and anthropogenic activities.
 --
 high with violin meteorological effects
--
Annual maximum in the winter for DZ and UB are from PM2.5, which results an increase in PM10.

clearly states that .... DZ and UB are from the ... household ., that concentration can be as high as a arctic oscillation/Siberian high intensifies with the heating, as low as it loose or may combination of heating demand drops.

[BUT]

[THEREFORE] PM10 and PM2.5 concentrations are larger in the spring followed by the autumn for SS and ZU sites. Annual PM10 and PM2.5 concentrations peaks in the winter aligned with the daily variations happens at the heating time for SS and ZU sites. This points that the increase in PM2.5 and PM10 is from the coal combustion.
It requires the cause the behind such the variations. DZ site is polluted in the winter by the heating and in the spring by the natural dust.

3.  Do PM2.5 particulates has contributed to the PM10 annual
    variations?
      Distinct temporal variations has existed among the sites.
        -   PM2.5 particulates has contributed to the PM10 annual
            variations in UB and in DZ in winter.
            -   If yes, how much, and when and where?
            -   What is the sd, mean, and median
                -   box plot
                -   violin
                -   scatter points, epidemic, sporadic
            -   Daily variations to examine it related to the heating
                -   2 peaks: smaller and bigger
                -   compare the t-duration exceeds 50mug/m3/hour

@@

[AND] To distinguish the emission driving variables, at first we demonstrated interrelations between wind speed, visibility among particulate matters of PM10 and PM2.5 for each sites (figure_4).

Figure 6 illustrates the relationship between PM10 and PM2.5 concentrations across the four sites (UB, DZ, ZU, and SS) for different seasons, alongside variations in wind speed (WS) and visibility (VIS). At all sites, a strong positive correlation between PM10 and PM2.5 is evident, as highlighted by the linear trendlines. The slopes suggest proportionality, with PM2.5 typically contributing a significant fraction of PM10 concentrations.

Seasonal differences are prominent, with higher PM concentrations observed during November-February (marked as $"+"$ symbols), particularly at UB and DZ, where values significantly exceed those from other periods. Wind speed and visibility also exhibit notable interactions; higher PM concentrations tend to correspond to lower wind speeds (smaller circles) and reduced visibility (darker blue points). Conversely, during March–June and July–October, marked by circles and triangles, respectively, the overall concentrations are lower, especially at ZU and SS, indicating better air quality conditions likely due to more favorable meteorological factors.

The site DZ shows the largest variability in PM concentrations, with extreme outliers during high-pollution periods. SS, on the other hand, exhibits relatively low PM levels across all seasons, aligning with its less polluted status. These results underscore the importance of local factors, including meteorological conditions and emission sources, in driving the observed PM dynamics.

### 2024-11-22 submission/manuscript.tex
draft processing

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\documentclass[
  11pt,
]{article}
\usepackage{xcolor}
\usepackage[margin=1.0in]{geometry}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\usepackage{helvet} % Helvetica font
\renewcommand*\familydefault{\sfdefault} % Use the sans serif version of the font
\usepackage[T1]{fontenc}

@@

Munkh\^{}1, Joeseph P. Schmo\^{}2, Sally J. Rivers\^{}1, Patrick D.
Schloss\textsuperscript{1}\(\dagger\)

@@

\(\dagger\) To whom correspondence should be addressed:
\href{mailto:pschloss@umich.edu}{\nolinkurl{pschloss@umich.edu}}

1. Department of Microbiology and Immunology, University of Michigan,
Ann Arbor, MI 48109

2. Other department contact information

@@

\subsection{Abstract}\label{abstract}

@@

@@

To comparatively examine the spatio-difference regarding to the
emissions of PMs, we illustrated the hourly observed values of PM10 and
PM2.5 for all sites (figure\_3). On each site, PM10 is more sporadic
than PM2.5 due to dust epidemic nature. In conjunction, the mean values
averaged from hourly values are larger than its median concentrations
both on PM10 and PM2.5 for all sites. The mean variables of p-value show
that concentrations of particulate matters significantly differ with
99\% confident levels at all sites (figure\_3), except 95\% confident
level between DZ and UB on PM10 (figure\_3a). It clearly exhibits
general variations of particulate matters as expected and emphasizes
that the significant difference in the concentration values among the
sites. Besides all sites are quantitatively differ by the values of
concentrations in particulate matters, there are two main
characteristics can be seen when we compare the median deviations from
its mean values etc.

\begin{itemize}
\tightlist
\item
  such patterns are strongly manifested in ZU and SS sites.\\
\item
  the mean values those averaged from hourly concentrations of PM10 and
  PM2.5 is larger than its median are strongly manifested for all in UB
  and DZ sites.
\item
  Additionally, consider the significance of the ..
\end{itemize}

This highlight that the fine and coarse particulate matters
significantly vary among sites of urban and rural sites, and even within
Gobi (rural) sites. Moreover, \ldots. has a diversely characteristically
diversified in respect with the PM2.5 (fine) to PM10 (coarse)
particulates.,. which requires urban impacts

To reveal the natural and anthropogenic impacts on the concentrations of
particulate matters, we demonstrated annual variations of PM10 and PM2.5
for each sites (figure\_4). 3. Do PM2.5 particulates has contributed to
the PM10 annual variations? Distinct temporal variations has existed
among the sites. - PM2.5 particulates has contributed to the PM10 annual
variations in UB and in DZ in winter. - If yes, how much, and when and
where? - What is the sd, mean, and median - box plot - violin - scatter
points, epidemic, sporadic - Daily variations to examine it related to
the heating - 2 peaks: smaller and bigger - compare the t-duration
exceeds 50mug/m3/hour

{[}Therefore{]} SS and ZU sites are mainly affected by the spring dust,
followed by the autumn dust. Annual maximum in the winter for DZ and UB
are from PM2.5, which results an increase in PM10. It requires the cause
the behind such the variations. DZ site is polluted in the winter by the
heating and in the spring by the natural dust.

{[}Therefore{]} Spatio-temporally in two class; consists of 2 Gobi
sites, and 1 urban plus urbanized Gobi sites.

@@

\begin{verbatim}
    -   PMs varies with the wind speed and visibility
    -   In general, three distinct patterns were resulted with PCA
        analysis, which is in consistent with temporal variation.
        explained with variables and changes in drivings (with PCA
        analysis)
\end{verbatim}

@@

@@

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\documentclass[
  11pt,
]{article}
\usepackage{xcolor}
\usepackage[margin=1.0in]{geometry}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\usepackage{helvet} % Helvetica font
\renewcommand*\familydefault{\sfdefault} % Use the sans serif version of the font
\usepackage[T1]{fontenc}

@@

Munkhtsetseg\^{}1\^{}5\(^*\), Shimizu. A\^{}2, Matsuki. A\^{}3, Batdorj.
D\^{}4, Matsui. H\^{}1\(^*\)

@@

\(^*\) To whom correspondence should be addressed:
\href{mailto:e.munkhtsetseg@yahoo.com}{\nolinkurl{e.munkhtsetseg@yahoo.com}}

1. Nagoya University, Japan

2. NIES

@@

\subsection{Abstract (150 words)}\label{abstract-150-words}

@@

\begin{verbatim}
* Advanced the knowledge of global dust, has reached to recognize the sources,.
  - Classification dust brown color, seasonal characteristics, with coarse fractions.
  - This knowledge further efficient to climate system when elaborating dust-aerosol effects.
  - But, a large uncertainties in the global dust model has existed so for climate models which clearly limits our understanding the climate system and shape the facing global issues of global warming.
  - This is mainly caused by the lack of parameterization and recognition of iterative changes controlled by the natural forces and anthropogenic drivings.

* Mongolian dust brown color, seasonal characteristics, with coarse fractions.
  - Mongolian dust has an attention of the its mass fraction in global dust, yet unlikely elaborated in the climate models due to its majority of coarse fraction for its a small contribution to the climate system through its radiative feedback.
  - But, such recognized characterization might get no longer valid due to recent change in the driving of the emissions of air particulate matters. A large high concentrations of PM2.5 in the capital city of Mongolia has been observed  as a result of the heavy consumptions of coal as a winter heating has rapidly spread as a mining industry taken off since 2000. Winter weather stagnant conditions governed by the Siberian magnifies the concentrations of the particulate matter emissions by trapping the polluted air below the boundary layer, so that results in a very large high concentrations of PM2.5, locally. Even  recognized as one of the highly polluted capital cities in the world.
  - Therefore, It is important to examine the emerging changes and shifting patterns of air particulate matters in Mongolia. More importantly, it is essential to reveal the significant changes in the the altered fraction particularly, in the dust seasons considering its high potential of intriuging in the free atmosphere to transported in the long-distance, so carrying capacity of the role to shift the global climate system, and its side impacts on downwind regions.
\end{verbatim}

\begin{itemize}
\tightlist
\item
  Study goal

  \begin{itemize}
  \tightlist
  \item
    We hypothesize \ldots{}
  \item
    Our study will benefit not only to the global dust research but also
    climate, and further to the country itself for urban planning, and
    coal combustion.
  \end{itemize}
\end{itemize}

@@

\subsection{To evaluate the spatial variations in particulate matter
(PM) concentrations, we displayed hourly observed values of PM10 and
PM2.5 for all study sites (figure\_3). The mean p-values indicate that
PM concentrations differ significantly at a 99\% confidence level across
all sites (figure\_3), with the exception of a 95\% confidence level
between DZ and UB for PM10 (figure\_3a), highlighting substantial
concentration disparities among sites. While quantitative differences in
PM concentration values exist across all sites, two key patterns emerge
when examining median deviations from mean values and irregular
observation fluctuations. For instance, PM10 demonstrates more erratic
behavior than PM2.5 at each location, particularly evident at ZU and SS
sites. Furthermore, the mean values calculated from hourly measurements
surpass the median concentrations for both PM10 and PM2.5 across all
sites, with notable prominence at UB and DZ locations. Consequently,
significant spatial differences in PM concentrations exist among all
sites, regardless of urban or rural classification. However, the sites
can be categorized into two groups based on their characteristics: UB
(urban) and DZ (rural town, Gobi); and SS (rural, Gobi) and ZU (rural,
Gobi). These findings for DZ appear to support our hypothesis of
emerging new emission patterns related to increased coal consumption
during winter
months.}\label{to-evaluate-the-spatial-variations-in-particulate-matter-pm-concentrations-we-displayed-hourly-observed-values-of-pm10-and-pm2.5-for-all-study-sites-figure_3.-the-mean-p-values-indicate-that-pm-concentrations-differ-significantly-at-a-99-confidence-level-across-all-sites-figure_3-with-the-exception-of-a-95-confidence-level-between-dz-and-ub-for-pm10-figure_3a-highlighting-substantial-concentration-disparities-among-sites.-while-quantitative-differences-in-pm-concentration-values-exist-across-all-sites-two-key-patterns-emerge-when-examining-median-deviations-from-mean-values-and-irregular-observation-fluctuations.-for-instance-pm10-demonstrates-more-erratic-behavior-than-pm2.5-at-each-location-particularly-evident-at-zu-and-ss-sites.-furthermore-the-mean-values-calculated-from-hourly-measurements-surpass-the-median-concentrations-for-both-pm10-and-pm2.5-across-all-sites-with-notable-prominence-at-ub-and-dz-locations.-consequently-significant-spatial-differences-in-pm-concentrations-exist-among-all-sites-regardless-of-urban-or-rural-classification.-however-the-sites-can-be-categorized-into-two-groups-based-on-their-characteristics-ub-urban-and-dz-rural-town-gobi-and-ss-rural-gobi-and-zu-rural-gobi.-these-findings-for-dz-appear-to-support-our-hypothesis-of-emerging-new-emission-patterns-related-to-increased-coal-consumption-during-winter-months.}

{[}AND{]} To examine the PM emerging patterns whether it related to
household heating fuel, we demonstrated annual variations in PM10 and
PM2.5 concentrations at the sites. {[}AND{]} Significant annual
variations in PM10 and PM2.5 levels demonstrating higher concentrations
in colder months and lower concentrations in warmer months at UB and DZ
sites.

{[}AND{]} During colder months (January, November, December), PM10
concentrations contributed by elevated levels in PM2.5 were exceed 100
\(\mu g/m^3\), accompanied by PM10 and PM2.5 concentrations reached
their lowest points during warmer months (May-September), with medians
and ranges consistently below 50 \(\mu g/m^3\). This distinct seasonal
trend, peaking during the same cold months are supported by the diurnal
variations in PM10 and PM2.5 concentrations at sites DZ and UB. A
pronounced daily cycle is evident, at both DZ and UB sites, where PM
concentrations peak during nighttime and early morning hours
(approximately 8 PM to 4 AM UTC), with median values surpassing 50
\(\mu g/m^3\). PM2.5 concentrations consistently follow a similar
pattern but remain lower than PM10. In contrast, both pollutants exhibit
reduced concentrations during daytime hours (8AM to 4PM UTC), likely due
to increased atmospheric dispersion. At site UB, a comparable daily
trend is observed, but with lower overall concentrations and less
pronounced peaks. The variability, indicated by the interquartile range,
is higher during nighttime, suggesting the influence of localized
emission sources and reduced boundary layer mixing. These diurnal
patterns underscore the temporal dynamics of air pollution, influenced
by both anthropogenic activities and meteorological conditions.

\begin{longtable}[]{@{}l@{}}
\toprule\noalign{}
nalysis of PM10 and PM2.5 concentrations revealed that ZU and SS
maintained significantly lower levels throughout the year, while UB and
DZ exhibited higher concentrations, especially during colder months. The
consistently lower particulate matter levels at ZU and SS suggest
localized differences in pollution sources and dispersion patterns.
These results underscore the seasonal and spatial variability in air
quality, likely influenced by meteorological conditions and human
activities. The observed seasonal patterns in PM10 and PM2.5
concentrations may be attributed to changes in weather conditions and
anthropogenic activities. \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
high with violin meteorological effects \\
\end{longtable}

Annual maximum in the winter for DZ and UB are from PM2.5, which results
an increase in PM10.

clearly states that \ldots. DZ and UB are from the \ldots{} household .,
that concentration can be as high as a arctic oscillation/Siberian high
intensifies with the heating, as low as it loose or may combination of
heating demand drops.

{[}BUT{]}

{[}THEREFORE{]} PM10 and PM2.5 concentrations are larger in the spring
followed by the autumn for SS and ZU sites. Annual PM10 and PM2.5
concentrations peaks in the winter aligned with the daily variations
happens at the heating time for SS and ZU sites. This points that the
increase in PM2.5 and PM10 is from the coal combustion. It requires the
cause the behind such the variations. DZ site is polluted in the winter
by the heating and in the spring by the natural dust.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\tightlist
\item
  Do PM2.5 particulates has contributed to the PM10 annual variations?
  Distinct temporal variations has existed among the sites. - PM2.5
  particulates has contributed to the PM10 annual variations in UB and
  in DZ in winter. - If yes, how much, and when and where? - What is the
  sd, mean, and median - box plot - violin - scatter points, epidemic,
  sporadic - Daily variations to examine it related to the heating - 2
  peaks: smaller and bigger - compare the t-duration exceeds
  50mug/m3/hour
\end{enumerate}

@@

{[}AND{]} To distinguish the emission driving variables, at first we
demonstrated interrelations between wind speed, visibility among
particulate matters of PM10 and PM2.5 for each sites (figure\_4).

Figure 6 illustrates the relationship between PM10 and PM2.5
concentrations across the four sites (UB, DZ, ZU, and SS) for different
seasons, alongside variations in wind speed (WS) and visibility (VIS).
At all sites, a strong positive correlation between PM10 and PM2.5 is
evident, as highlighted by the linear trendlines. The slopes suggest
proportionality, with PM2.5 typically contributing a significant
fraction of PM10 concentrations.

Seasonal differences are prominent, with higher PM concentrations
observed during November-February (marked as \("+"\) symbols),
particularly at UB and DZ, where values significantly exceed those from
other periods. Wind speed and visibility also exhibit notable
interactions; higher PM concentrations tend to correspond to lower wind
speeds (smaller circles) and reduced visibility (darker blue points).
Conversely, during March--June and July--October, marked by circles and
triangles, respectively, the overall concentrations are lower,
especially at ZU and SS, indicating better air quality conditions likely
due to more favorable meteorological factors.

The site DZ shows the largest variability in PM concentrations, with
extreme outliers during high-pollution periods. SS, on the other hand,
exhibits relatively low PM levels across all seasons, aligning with its
less polluted status. These results underscore the importance of local
factors, including meteorological conditions and emission sources, in
driving the observed PM dynamics.

@@

\begin{itemize}
\tightlist
\item
  PMs varies with the wind speed and visibility
\item
  In general, three distinct patterns were resulted with PCA analysis,
  which is in consistent with temporal variation. explained with
  variables and changes in drivings (with PCA analysis)
\end{itemize}

@@

\subsubsection{Materials}\label{materials}

\subsubsection{Methods 3,000 words}\label{methods-3000-words}

\subsection{Acknowledgements}\label{acknowledgements}

Keep acknowledgements brief and do not include thanks to anonymous
referees or editors, or effusive comments. Grant or contribution numbers
may be acknowledged.

\subsection{Figures (10)}\label{figures-10}

Figure legends should be \textless350 words each. They should begin with
a brief title sentence for the whole figure and continue with a short
statement of what is depicted in the figure, not the results (or data)
of the experiment or the methods used. Legends should be detailed enough
so that each figure and caption can, as far as possible, be understood
in isolation from the main text.

Tables. Each table should be prepared using the Table menu in Word or
the table environment in TeX/LaTeX and accompanied by a short title
sentence describing what the table shows. Further details can be
included as footnotes to the table.

\subsection{References (70)}\label{references-70}

\subsection{Supplementary}\label{supplementary}

Author contributions. You must include a statement that specifies the
individual contributions of each co-author. For example: ``A.P.M.
`contributed' Y and Z; B.T.R. `contributed' Y,'' etc. See our authorship
policies for more details.

Competing interests. Submission of a competing interests statement is
required for all content of the journal.

Materials \& Correspondence. Indicate the author(s) to whom
correspondence and material requests should be addressed.

Supplementary information Please submit supplementary figures, small
tables and text as a single combined PDF document. Tables longer than
one page should be provided as an Excel or similar file type. For
optimal quality video files please use H.264 encoding, the standard
aspect ratio of 16:9 (4:3 is second best) and do not compress the video.
We encourage submission of step-by-step synthesis procedures for
chemical compounds and data on compound characterization. Supplementary
information is not copyedited, so please ensure that it is clearly and
succinctly presented, and that the style and terminology conform to the
rest of the manuscript.

\subsection{Materials and Methods}\label{materials-and-methods-1}
